---
title: "Lunch Analysis"
Author: "Mebarek"
output: pdf_document
---
```{r include = FALSE, message = FALSE, warning = FALSE}
# Load libraries
library(tidyverse)
library(reshape2)
library(ggplot2)
```
```{r include = FALSE, message = FALSE, warning = FALSE}
# Load the dataset
data <- read.csv("../data/study_performance_cleaned.csv")
```
# Performance and Lunch
## Math Scores
```{r}
# Perform t-test for math scores between students with standard lunch and free/reduced lunch
t_test_math_lunch <- t.test(math_score ~ lunch, data = data)
print(t_test_math_lunch)
```
## Reading Scores
```{r}
# Perform t-test for reading scores between students with standard lunch and free/reduced lunch
t_test_reading_lunch <- t.test(reading_score ~ lunch, data = data)
print(t_test_reading_lunch)
```
## Writing Scores
```{r}
# Perform t-test for writing scores between students with standard lunch and free/reduced lunch
t_test_writing_lunch <- t.test(writing_score ~ lunch, data = data)
print(t_test_writing_lunch)
```
Based on the Lunch Analysis, we can answer the following questions:

1. **Is there a difference in performance between students who have standard lunch and those who have free/reduced lunch?**

   The analysis indicates that there is a significant difference in the academic performance between students who have standard lunch and those who have free/reduced lunch:

    - **Math Scores**: The t-test results show a statistically significant difference in the mean math scores between the two groups (p-value < 2.2e-16). Students with standard lunch have a higher mean math score (70.23988) compared to students with free/reduced lunch (60.07849).
    - **Reading Scores**: The t-test results show a statistically significant difference in the mean reading scores between the two groups (p-value = 5.255e-11). Students with standard lunch have a higher mean reading score (71.84424) compared to students with free/reduced lunch (65.76453).
    - **Writing Scores**: The t-test results show a statistically significant difference in the mean writing scores between the two groups (p-value = 1.134e-12). Students with standard lunch have a higher mean writing score (71.02336) compared to students with free/reduced lunch (64.21512).

2. **Does the type of lunch have any impact on academic performance?**

   The analysis clearly indicates that the type of lunch (standard or free/reduced) has a significant impact on the academic performance of students across all three subjects:

    - The t-test results show that the differences in mean scores between the two lunch groups are statistically significant for math, reading, and writing.
    - Students who have standard lunch consistently outperform their peers who have free/reduced lunch in all three subjects.

These findings suggest that the type of lunch a student receives is an important factor that is associated with their academic performance. Students who have access to standard lunch, which is likely indicative of a higher socioeconomic status, tend to perform better academically compared to students who receive free or reduced-price lunch, which is often associated with a lower socioeconomic background.

In summary, the Lunch Analysis demonstrates that there is a significant difference in the academic performance of students based on the type of lunch they receive. Students with standard lunch outperform their peers with free/reduced lunch in math, reading, and writing. This suggests that the type of lunch can be a proxy for socioeconomic status and may have an impact on a student's academic outcomes.
