---
title: "Geospatial Mapping"
output: pdf_document
documentclass: article
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
---


```{r}
# Load necessary libraries
library(dplyr)
library(ggplot2)
library(ggmap)

incidents_data <- read.csv("data/police-department-incidents.csv")

# Check the structure of the dataset
str(incidents_data)
```
position the caret at any line or the code chunk, then click "+".
```{r}
# Load a static map of San Francisco
sf_map <- readRDS("data/sf_map.RDS")  # Load the preprocessed map
```
Plotting All Crime Incidents
```{r}
# Filter data for plotting
crime_data <- incidents_data %>%
  filter(!is.na(X) & !is.na(Y))  # Ensure there are no missing values in geospatial data

# Plot crime incidents on the map
ggmap(sf_map) +
  geom_point(data = crime_data, aes(x = X, y = Y, color = Category), alpha = 0.5, size = 1) +
  theme_minimal() +
  labs(title = "Crime Incidents in San Francisco",
       x = "Longitude",
       y = "Latitude") +
  theme(legend.position = "bottom")
```
Plotting Specific Crime Type (e.g., Theft)
```{r}
# Filter data for specific crime type (e.g., Theft)
theft_data <- crime_data %>%
  filter(Category == "Larceny/Theft")

# Plot theft incidents on the map
ggmap(sf_map) +
  geom_point(data = theft_data, aes(x = X, y = Y), alpha = 0.5, color = "red", size = 1) +
  theme_minimal() +
  labs(title = "Theft Incidents in San Francisco",
       x = "Longitude",
       y = "Latitude") +
  theme(legend.position = "none")
```
Density Plot for Crime Incidents
```{r}
# Density plot for all crime incidents
ggmap(sf_map) +
  stat_density2d(data = crime_data, aes(x = X, y = Y, fill = ..level..), geom = "polygon", alpha = 0.3) +
  scale_fill_gradient(low = "yellow", high = "red") +
  theme_minimal() +
  labs(title = "Crime Incident Density in San Francisco",
       x = "Longitude",
       y = "Latitude") +
  theme(legend.position = "bottom")
```

